### 2024-01-03 thesis/chapters/04-implementation.tex
Test SD card and DP2 export

The secondary pump is one unit named \emph{Sigma~300-OVD-600} (Fig.~\ref{fig:machine:pump-sigma}) installed in 1986. It rotates at 1485 rpm (24.75 Hz), and its electric motor has power of 450~kW. Each pump and motor have 2 bearings. Therefore, there are 4 measurement positions in total.

@@

\begin{table}[ht]
\renewcommand{\arraystretch}{1.2}
\centering
\begin{tabular}{|l|l|l|}
\hline
\textbf{Accelerometer}                           & \textbf{ADXL335} & \textbf{IIS3DWB}   \\ \hline
\textbf{Vendor}                                  & Analog Devices   & STMicroelectronics \\ \hline
\textbf{Bus}                                     & Analog           & SPI                \\ \hline
\textbf{Axis}                                    & 3                & 1 or 3             \\ \hline
\textbf{Range} (g)                               & $\pm$ 3          & $\pm$ 2 to 16      \\ \hline
\textbf{Bandwidth} (kHz)                         & 0.55             & 5 - 6.3            \\ \hline
\textbf{Sensitivity}                             & 300 mV/g         & 0.061 mg/LSB       \\ \hline
\textbf{Noise density} ($\mu g / \sqrt{\mathrm{Hz}}$ rms) & 150 - 300        & 75                 \\ \hline
\textbf{Microcontroller}                         & Beaglebone Black & ESP32-PoE-ISO      \\ \hline
\textbf{CPU SoC}                                 & TI Sitara AM3358 & ESP32-WROOM-32     \\ \hline
\textbf{Output data rate} (kHz)                  & 2.5              & 26.7               \\ \hline
\textbf{ADC resolution} (bit)                    & 12               & 16                 \\ \hline
\textbf{FIFO}                                    & -                & 3 kB (512 samples) \\ \hline
\end{tabular}
\caption{Hardware parameters of previous and proposed sensor units}
\label{tab:design:hw-sensors}
\end{table}

The IIS3DWB accelerometer is a cheap enough MEMS accelerometer that approaches industrial standards for vibration monitoring. An interface capable of higher speeds is needed to store all acceleration samples. Therefore, ESP32-PoE-ISO is chosen as a microcontroller development kit because it has an SD card slot connected via SD/MMC bus. The accelerometer uses an SPI bus with a maximum speed of 10 MHz that can be connected to any physical GPIO pin. The block diagram of the designed hardware device is in Figure~\ref{fig:design:block-diagram-hw}.

@@

\section{Preliminary measurements}
During the initial on-site inspections of machinery, we carried out preliminary measurements of vibration signals. Raw waveforms of acceleration for the fan, two different compressors, and the outer bearing on a pump in three axes are plotted in Figure~\ref{fig:design:preliminary-acceleration}. The acceleration rarely exceeds 1~g.

@@

Figure~\ref{fig:design:preliminary-velocity} documents the effort to obtain vibration velocity (as per ISO~20186) by integration with the composite trapezoidal rule. The significant drift after integration is eliminated by subtracting the mean of the envelope constructed using cubic interpolation of peaks. Envelopes must be tweaked further to achieve more accurate values.

@@

The orbital plot of the first harmonic frequency $f_{max} \pm 5\;\mathrm{Hz}$ in Figure~\ref{fig:design:orbital-analysis} allows us to check the sensor deviation out of the axis of rotation.

>>>>

The secondary pump is one unit named \emph{Sigma~300-OVD-600} (Fig.~\ref{fig:machine:pump-sigma}) installed in 1986. It rotates at 1485 rpm (24.75 Hz), and its electric motor has power of 450~kW (class~\rom{3}). Each pump and motor have 2 bearings. Therefore, there are 4 measurement positions in total.

@@

\begin{table}[ht]
\renewcommand{\arraystretch}{1.2}
\centering
\begin{tabular}{|l|l|l|}
\hline
\textbf{Accelerometer}                           & \textbf{ADXL335} & \textbf{IIS3DWB}   \\ \hline
\textbf{Vendor}                                  & Analog Devices   & STMicroelectronics \\ \hline
\textbf{Bus}                                     & Analog           & SPI                \\ \hline
\textbf{Axis}                                    & 3                & 1 or 3             \\ \hline
\textbf{Range} (g)                               & $\pm$ 3          & $\pm$ 2 to 16      \\ \hline
\textbf{Bandwidth} (kHz)                         & 0.55 - 1.6       & 5 - 6.3            \\ \hline
\textbf{Sensitivity} (mg/LSB)                    & 2.930            & 0.061       \\ \hline
\textbf{Noise density} ($\mu g / \sqrt{\mathrm{Hz}}$ rms) & 150 - 300        & 75                 \\ \hline
\textbf{Microcontroller}                         & Beaglebone Black & ESP32-PoE-ISO      \\ \hline
\textbf{CPU SoC}                                 & TI Sitara AM3358 & ESP32-WROOM-32     \\ \hline
\textbf{Output data rate} (kHz)                  & 2.5              & 26.7               \\ \hline
\textbf{ADC resolution} (bit)                    & 12               & 16                 \\ \hline
\textbf{FIFO}                                    & -                & 3 kB (512 samples) \\ \hline
\end{tabular}
\caption{Hardware parameters of previous and proposed sensor units}
\label{tab:design:hw-sensors}
\end{table}

The IIS3DWB accelerometer is a cheap enough MEMS accelerometer that approaches industrial standards for vibration monitoring. ESP32-PoE-ISO is chosen as a microcontroller development kit because it has an SD card slot connected via SD/MMC bus. It enables us to store all samples from FIFO. The accelerometer uses an SPI bus with a maximum speed of 10 MHz that can be connected to any physical GPIO pin. The block diagram of the designed hardware device is in Figure~\ref{fig:design:block-diagram-hw}.

@@

\section{Preliminary measurements}
During the initial on-site inspections of machinery, we carried out preliminary measurements of vibration signals. Raw waveforms of acceleration for the fan, two different compressors, and the outer bearing on a pump and motor in three axes are plotted in Figure~\ref{fig:design:preliminary-acceleration}. The acceleration rarely exceeds 1~g.

@@

Figure~\ref{fig:design:preliminary-velocity} documents the effort to obtain vibration velocity (as per ISO~20186) by integration with the composite trapezoidal rule. The significant drift after integration is eliminated by subtracting the mean of the envelope constructed using cubic interpolation of peaks. Envelopes must be tweaked further to achieve more accurate values. The orbital plot of the first harmonic frequency $f_{max} \pm 5\;\mathrm{Hz}$ in Figure~\ref{fig:design:orbital-analysis} allows us to check the sensor deviation out of the axis of rotation.

@@

### 2024-01-03 thesis/chapters/appendix/B-plan-of-work.tex
Test SD card and DP2 export

\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1} week         & Semester kickoff meeting to set goals, and experiments and discuss the status of collaborations with partners.
\\ \hline
\nth{2} week         &  Arrange collaboration with an alternative industry partner. Prepare a checklist for the technical inspection of machinery. Construct a device for exploratory measurements.
\\ \hline
\nth{3} week         & Technical inspection of air conditioning units in the data center. Feature extraction step to calculate features from MaFaulDa.
 \\ \hline
\nth{4} week         & Consultation about plan for machine to measure in the data center and better device for measurement.
 \\ \hline
\nth{5} week         &  In feature selection using various metrics to determine sets of best features in the MaFaulDa.
 \\ \hline
\nth{6} week         & Feature selection used in kNN multiclass and binary classificator.
 \\ \hline
\nth{7} week         & Explore incremental learning kNN algorithm with MaFaulDa dataset. Consultation and status report.
 \\ \hline
 \nth{8} week         & Shorten analysis chapter about wavelets. Look at clustering detection incremental learning in MaFaulDa.
 \\ \hline
 \nth{9} week         &  Refactor separate trials in feature selection to integrate them into the pipeline for kNN validation. Consultation to discuss progress.
 \\ \hline
  \nth{10} week         & Include incremental learning in analysis. Experiment with gradual feature selection in incremental learning. Fix the sampling rate issue in the provisional sensor unit.
 \\ \hline
  \nth{11} week         & Consultation in preparation for machine inspections. Preliminary measurements of fan, compressors, and pump.
 \\ \hline
  \nth{12} - \nth{15} week         &  Write up design chapter: research questions, visualization export. Finish writing chapter on design and implementation.
 \\ \hline
\end{tabular}
\end{table}

@@

\section{Summer semester - DP3}
\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1}  - \nth{2} week         & 
\begin{enumerate}
\itemsep0pt
\item Incorporate suggestions from DP2 defense. 
\item Develop and test firmware for designed sensor unit.
\end{enumerate}
\\ \hline
\nth{2}  - \nth{10} week         & 
\begin{enumerate}
\itemsep0pt
\item Long-term manual regular gathering of vibration data from compressors and pumps. 
\item Find optimal number of features. 
\item Try to increase kNN prediction metrics.
\item Put together incremental learning with feature selection. 
\item Explore incremental clustering in search of method that can help with labeling.
\end{enumerate}
\\ \hline
\nth{10} - \nth{12} week         & Conclude results from measurements in real environment.
 \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1} week         & Semester kickoff meeting to set goals, and experiments and discuss the status of collaborations with partners.
\\ \hline
\nth{2} week         &  Arrange collaboration with an alternative industry partner. Prepare a checklist for the technical inspection of machinery. Construct a device for exploratory measurements.
\\ \hline
\nth{3} week         & Technical inspection of air conditioning units in the data center. Feature extraction step to calculate features from MaFaulDa.
 \\ \hline
\nth{4} week         & Consultation about plan for machine to measure in the data center and better device for measurement.
 \\ \hline
\nth{5} week         &  In feature selection using various metrics to determine sets of best features in the MaFaulDa.
 \\ \hline
\nth{6} week         & Feature selection used in KNN multiclass and binary classificator.
 \\ \hline
\nth{7} week         & Explore incremental learning KNN algorithm with MaFaulDa dataset. Consultation and status report.
 \\ \hline
 \nth{8} week         & Shorten analysis chapter about wavelets. Look at clustering detection incremental learning in MaFaulDa.
 \\ \hline
 \nth{9} week         &  Refactor separate trials in feature selection to integrate them into the pipeline for kNN validation. Consultation to discuss progress.
 \\ \hline
  \nth{10} week         & Include incremental learning in analysis. Experiment with gradual feature selection in incremental learning. Fix the sampling rate issue in the provisional sensor unit.
 \\ \hline
  \nth{11} week         & Consultation in preparation for machine inspections. Preliminary measurements of fan, compressors, and pump.
 \\ \hline
  \nth{12} - \nth{15} week         &  Write up design chapter: research questions, visualization export. Finish writing chapter on design and implementation.
 \\ \hline
\end{tabular}
\end{table}

@@

\section{Summer semester - DP3}
\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1}  - \nth{2} week         & 
\begin{enumerate}
\itemsep0pt
\item Incorporate suggestions from DP2 defense. 
\item Develop and test firmware for designed sensor unit.
\end{enumerate}
\\ \hline
\nth{2}  - \nth{10} week         & 
\begin{enumerate}
\itemsep0pt
\item Long-term manual regular gathering of vibration data from compressors and pumps. 
\item Find optimal number of features. 
\item Try to increase KNN prediction metrics.
\item Put together incremental learning with feature selection. 
\item Explore incremental clustering in search of method that can help with labeling.
\end{enumerate}
\\ \hline
\nth{10} - \nth{12} week         & Conclude results from measurements in real environment.
 \\ \hline
\end{tabular}
\end{table}
